Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-13 paper/paper.tex
quick pass on evaluation

\vspace{2ex}
\noindent\textbf{Limitation.} It is worth noting that although
\tname{} is accurate for generating rules that discrimate positive and
negative traffic, the quality of these rules is limited by the quality
of the training data it uses. For the positive traffic, \tname{} only
requires one sample, but can benefit of several samples as the example
from Section~\ref{sec:dos} illustrated. The same applies for the
negative traffic. In this case, however, \tname{} can use public
datasets available online.

@@

\subsection{Objects of Analysis}

Table~\ref{table:attacks} shows the attacks we analyzed and the
options of the rule from the Emerging Threats Open
Ruleset~\cite{emerging-threats-open} that captures the attack. Column
``Name'' shows the name of the attack, column ``Protocol'' shows the
protocol name, and column ``Ground Truth'' shows the options of the
rule that captures the attack.

@@

\subsection{Dataset of Benign Traffic}
\label{sec:dataset-benign}

Note from Figure~\ref{fig:overview} that the positive traffic is an
input to the technique. The negative non-malicious traffic, however,
is not. \tname{} uses public databases storing different kinds of
positive traffic for all protocols covered by Suricata. We used two
datasets of positive traffic. The Bigflows.pcap dataset is part of the
TcpReplay~\cite{tcpreplay} open source project. This dataset includes
real network traffic on a busy private network access point to the
Internet. According to the TcpReplay web site ``This capture is much
larger and has a smaller average packet size than the previous capture
(smallFlows.pcap). It also has many more flows and different
applications.''. In addition to the Bigflows.pcap dataset, we also
used datasets of normal traffic made available by Stratosphere
Lab~\cite{stratosphere-normal}.

@@

\tname{} expects (a) message(s) reproducing an attack on input. As
previously discussed, those messages could be directly provided by an
anomaly-based \nids\ tool. To evaluate \tname{}, however, we created
those messages ourselves. For all attacks listed on
Table~\ref{table:attacks}, we found reproduction scripts available on
the web. With the script to reproduce the attack, we proceeded as
follows: 1)~we instantiated the script on a given target machine,
2)~we executed the script, 3)~we monitored the traffic with the
wireshark network monitor~\cite{wireshark-net-monitor}, and 4) we
simulated the delivery of the corresponding network messages by
directly executing Suricata on the ``pcap'' files that wireshark
produced in the previous step. It is worth noting that Suricata is
invoked multiple times in the process of minimizing the rule (see
Section~\ref{sec:minimization}) and that processing pcap files is much
more efficient compared to sending and processing network messages. To
illustrate, the SYN Flood attack was reproduced with the hping3
tool~\cite{hping3} using the following command \CodeIn{hping3 -d 80 -w
  64 -S -p 80 --flood --rand-source <IP>}.

>>>>

\vspace{2ex}
\noindent\textbf{Limitations.} It is worth noting that although
\tname{} is accurate for generating rules that discrimate positive and
negative traffic, the quality of these rules is limited by the quality
of the training data it uses. For the positive traffic, \tname{} only
requires one sample, but can benefit of several samples as the example
from Section~\ref{sec:dos} illustrated. The same applies for the
negative traffic. In this case, however, \tname{} can use public
datasets available online.

@@

\subsection{Objects of Analysis}
\label{sec:dataset-benign}

Table~\ref{table:attacks} shows the attacks we considered in our
evaluation. These attacks cover different protocols and features of
\tname{}. Column ``Name'' shows the name of the attack, column
``Protocol'' shows the protocol name, and column ``Ground Truth''
shows the options of the rule that captures the attack.

\vspace{1ex}
\noindent
\textbf{Malicious traffic.}~Nikito?\Fix{where do these
  attacks/messages come from?}

\vspace{1ex}
\noindent
\textbf{Benign traffic.}~\tname{} uses public databases storing benign
traffic for all protocols covered by Suricata (see
Figure~\ref{fig:distribution-rules-protocol}). We used two datasets of
positive traffic. The Bigflows.pcap dataset is part of the
TcpReplay~\cite{tcpreplay} open source project. This dataset includes
real network traffic on a busy private network access point to the
Internet. According to the TcpReplay web site ``This capture is much
larger and has a smaller average packet size than the previous capture
(smallFlows.pcap). It also has many more flows and different
applications.''. In addition to the Bigflows.pcap dataset, we also
used datasets of normal traffic made available by Stratosphere
Lab~\cite{stratosphere-normal}.

\vspace{1ex}
\noindent
\textbf{Ground Truth.}~The rules that detect those attacks were
obtained from the Emerging Threats Open
Ruleset~\cite{emerging-threats-open}.

%% Note from Figure~\ref{fig:overview} that the positive traffic is an
%% input to the technique. The negative non-malicious traffic, however,
%% is not.

@@

@@

\subsubsection{Attack reproduction.} \tname{} requires the attack to
be replayed in order to check whether or not the rule it generates
captures the attack.  See function $\mathit{isPlausible}$, used in the
minimization algorithm from Section~\ref{sec:minimization}. For all
attacks listed on Table~\ref{table:attacks}, we found scripts
available on the web to replay the attacks. For example, the SYN Flood
attack can be replayed with hping3~\cite{hping3}, using the following
command: \CodeIn{hping3 -d 80 -w 64 -S -p 80 --flood --rand-source
  <IP>}. With the script to reproduce the attack, we executed the
following steps to obtain ``pcap'' files, which abstracts network
messages~\cite{pcap}, to run \tname:~1)~instantiate the script (\eg{},
define the IP, for the example above), 2)~execute the script,
3)~monitor the traffic with the wireshark network
monitor~\cite{wireshark-net-monitor}.

Recall that Suricata is invoked multiple times in the process of
minimizing the rule (see Section~\ref{sec:minimization}). Suricata
supports a feature to process ``pcap'' files, enabling very efficient
performance compared to processing actual network messages.
